---
title: "ReThinking Emergency Rental Allocation"
subtitle: "Appendix C. Econometric models and variables descriptors"
author: 
- "ReThinkers"
- "Regina Isabel Medina Rosales, Sanhitha Cherukupally,"
- "Tasaduq, Carlos Enrique Huapaya"

date: "October 16th, 2022"
output: 
  rmarkdown::pdf_document:
    toc: true
    latex_engine: xelatex
---

    
\usepackage{fancyhdr}
\pagestyle{fancy}
% center of header
\fancyhead[CO,CE]{Your Document Header}
% center of footer
\fancyfoot[CO,CE]{And this is a fancy footer}
% page number on the left of even pages and right of odd pages
\fancyfoot[LE,RO]{\thepage}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Being at risk of eviction is a result of several factors. Recognizing the multicasual nature of this social phenomenon, the _ReThinkers_ team designed a quantitative strategy sensitive to both personal-level factors and state-level factors. 

## Person-level factors 

### Data sources and variables descriptors  

### Econometric model 

### Results 


```{r cars}
summary(cars)
```

## State-level factors 

### Data sources and variables descriptors  

### Econometric model 

### Results


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
